Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2025-07-05 manuscript/Suppl_material/supplementary.Rmd
changes to suppl. material

Studying the effect of stimulus-onset-asynchrony (SOA) on mean RT is still a popular approach to study the time course of cognitive processes (ref). For example, a target stimulus can be presented with a certain SOA in relation to another stimulus (e.g., prime, mask, distractor, cue). However, mean RT conceals the possibe presence of responses triggered by the non-target stimulus (Panis, 2020; Panis & Schmidt, 2016). For example, in Supplementary Figure 1C a prime is presented before a target with a SOA of -400 ms (upper x-axis labels). To capture responses triggered by the prime (and emitted before target onset) we have to start the timer at trial onset. Also, when RTs are originally recorded relative to target onset, we have to add a constant time to each (here: + 400 ms) in order to include these "negative" RTs in the analysis (lower x-axis labels). In general, all RTs must be positive for EHA to work.

Finally, in a bistable perception task (Supplementary Figure 1D), the participant is looking at an ambiguous stimulus (e.g., the duck-rabbit illusion, the Necker cube) for two minutes in each trial, for example, and asked to press a button each time when her/his perception switches from one possibe interpretation to the other possible interpretation. In this task, there are two events (percept A switches to percept B, percept B switches to percept A) that can recur within the same observation period of two minutes, so that the individual transitions back and forth between two states. Note that we do not analyse recurrent events in this tutorial. More information about recurrent events analysis can be found in REF and REF...

@@

The shape of a distribution of waiting times can be described in multiple ways [@luceResponseTimesTheir1991]. After dividing time in discrete, contiguous time bins indexed by t, let RT be a discrete random variable denoting the rank of the time bin in which a particular person's response occurs in a particular experimental condition. 
Because waiting times can only increase, discrete-time EHA focuses on the discrete-time hazard function

@@

While psychological RT data is typically measured in small, continuous units (e.g., milliseconds), discrete-time EHA treats the RT data as interval-censored data, because it only uses the information that the response occurred sometime in a particular bin of time (x,y]: x < RT $\leq$ y. If we want to use the exact event times, then we treat time as a continuous variable, and let RT be a continous random variable denoting a particular person's response time in a particular experimental condition. Continuous-time EHA does not focus on the cumulative distribution function F(t) = P(RT $\leq$ t) and its derivative, the probability density function f(t) = F(t)', but on the survivor function S(t) = P(RT $>$ t) and the hazard rate function $\lambda$(t) = f(t)/S(t). The hazard rate function gives you the instantaneous *rate* of event occurrence at time point t, given that the event has not occurred yet.

@@

Popular link functions include the logit link and the complementary log-log link, as shown in Supplementary Figure 1.

(ref:descr-plot14-caption) The logit and cloglog link functions.

@@

An example (single-level) discrete-time hazard model with three predictors (TIME, X~1~, X~2~), the cloglog link function, and a second-order polynomial specification for TIME can be written as follows:

\noindent cloglog[h(t)] = ln(-ln[1-h(t)]) =  [$\beta$~0~ONE + $\beta$~1~(TIME-9) + $\beta$~2~(TIME-9)$^2$] +                                    [$\beta$~3~X~1~ + $\beta$~4~X~2~ + $\beta$~5~X~2~(TIME-9)]  \hfill  (6)

The main predictor variable TIME is the time bin index t that is centered on value 9 in this example. The first set of terms within brackets, the parameters $\beta$~0~ to $\beta$~2~ multiplied by their polynomial specifications of (centered) time, represents the shape of the baseline cloglog-hazard function (i.e., when all predictors X~i~ take on a value of zero). The second set of terms (the beta parameters $\beta$~3~ to $\beta$~5~) represents the vertical shift in the baseline cloglog-hazard for a 1 unit increase in the respective predictor variable. Predictors can be discrete, continuous, and time-varying or time-invariant. For example, the effect of a 1 unit increase in X~1~ is to vertically shift the whole baseline cloglog-hazard function by $\beta$~3~ cloglog-hazard units. However, if the predictor interacts linearly with TIME (see X~2~ in the example), then the effect of a 1 unit increase in X~2~ is to vertically shift the predicted cloglog-hazard in bin 9 by $\beta$~4~ cloglog-hazard units (when TIME-9 = 0), in bin 10 by $\beta$~4~ + $\beta$~5~ cloglog-hazard units (when TIME-9 = 1), and so forth. To interpret the effects of a predictor, its $\beta$ parameter is exponentiated, resulting in a hazard ratio (due to the use of the cloglog link). When using the logit link, exponentiating a $\beta$ parameter results in an odds ratio.

An example (single-level) discrete-time hazard model with a general specification for TIME (separate intercepts for each of six bins, where D1 to D6 are binary indicator variables identifying each bin) and a single predictor (X~1~) can be written as follows:

\noindent cloglog[h(t)] =  [$\beta$~0~D1 + $\beta$~1~D2 + $\beta$~2~D3 + $\beta$~3~D4 + $\beta$~4~D5 + $\beta$~5~D6] + [$\beta$~6~X~1~]  \hfill  (7)

@@

To gain a sense of what prior *logit* values would approximate a uniform distribution on the probability scale, @kurzAppliedLongitudinalDataAnalysis2023 simulated a large number of draws from the Uniform(0,1) distribution, converted those draws to the log-odds metric, and fitted a Student's t distribution. Row C in Supplementary Figure 2 shows that using a t-distribution with 7.61 degrees of freedom and a scale parameter of 1.57 as a prior on the logit scale, approximates a uniform distribution on the probability scale. According to @kurzAppliedLongitudinalDataAnalysis2023, such a prior might be a good prior for the intercept(s) in a logit-hazard model, while the N(0,1) prior in row D might be a good prior for the non-intercept parameters in a logit-hazard model, as it gently regularizes p towards .5 (i.e., a zero effect on the logit scale).

@@

## G. Advantages of hazard analysis

>>>>

Studying the effect of stimulus-onset-asynchrony (SOA) on mean RT is still a popular approach to study the time course of cognitive processes. For example, a target stimulus can be presented with a certain SOA in relation to another stimulus (e.g., prime, mask, distractor, cue). However, mean RT conceals the possibe presence of responses triggered by the non-target stimulus (Panis, 2020; Panis & Schmidt, 2016). For example, in Supplementary Figure 1C a prime is presented before a target with a SOA of -400 ms (upper x-axis labels). To capture responses triggered by the prime (and emitted before target onset) we have to start the timer at trial onset. Also, when RTs are originally recorded relative to target onset, we have to add a constant time to each (here: + 400 ms) in order to include these "negative" RTs in the analysis (lower x-axis labels). In general, all RTs must be positive for EHA to work.

Finally, in a bistable perception task (Supplementary Figure 1D), the participant is looking at an ambiguous stimulus (e.g., the duck-rabbit illusion, the Necker cube) for two minutes in each trial, for example, and asked to press a button each time when her/his perception switches from one possibe interpretation to the other possible interpretation. In this task, there are two events (percept A switches to percept B, percept B switches to percept A) that can recur within the same observation period of two minutes, so that the individual transitions back and forth between two states. Note that we do not analyse recurrent events in this tutorial. More information about recurrent events analysis can be found in @stoolmillerModelingHeterogeneitySocial2006 and @millsIntroducingSurvivalEvent2011.

@@

The shape of a distribution of waiting times can be described in multiple ways [@luceResponseTimesTheir1991]. After dividing time in discrete, contiguous time bins indexed by t, let RT be a discrete random variable denoting the rank of the time bin in which a particular person's response occurs in a particular trial. 
Because waiting times can only increase, discrete-time EHA focuses on the discrete-time hazard function

@@

While psychological RT data is typically measured in small, continuous units (e.g., milliseconds), discrete-time EHA treats the RT data as interval-censored data, because it only uses the information that the response occurred sometime in a particular bin of time (x,y]: x < RT $\leq$ y. If we want to use the exact event times, then we treat time as a continuous variable, and let RT be a continous random variable denoting a particular person's response time in a particular experimental condition. Continuous-time EHA does not focus on the cumulative distribution function F(t) = P(RT $\leq$ t) and its derivative, the probability density function f(t) = F(t)', but on the survivor function S(t) = P(RT $>$ t) and the hazard rate function $\lambda$(t) = f(t)/S(t). The hazard rate function gives you the instantaneous *rate* of event occurrence at time point t, given that the event has not occurred yet. Models for continous-time event data come in three forms: parametric models, Cox regression, and piece-wise exponential models [@singerAppliedLongitudinalData2003].

@@

Popular link functions include the logit link and the complementary log-log link, as shown in Supplementary Figure 2.

(ref:descr-plot14-caption) The logit and complementary log-log (cloglog) link functions.

@@

An example (single-level) discrete-time hazard model for individual i in bin t of trial j with three predictors (TIME, X~1~, X~2~), the cloglog link function, and a second-order polynomial specification for TIME can be written as follows:

\noindent cloglog[h~ij~(t)] = ln(-ln[1-h~ij~(t)]) =  [$\beta$~0~ONE + $\beta$~1~(TIME-9) + $\beta$~2~(TIME-9)$^2$] +                                    [$\beta$~3~X~1ij~ + $\beta$~4~X~2ij~ + $\beta$~5~X~2ij~(TIME-9)]  \hfill  (6)

The main predictor variable TIME is the time bin index t that is centered on value 9 in this example. The first set of terms within brackets, the parameters $\beta$~0~ to $\beta$~2~ multiplied by their polynomial specifications of (centered) time, represents the shape of the baseline cloglog-hazard function (i.e., when all predictors X~ij~ take on a value of zero). The second set of terms (the beta parameters $\beta$~3~ to $\beta$~5~) represents the vertical shift in the baseline cloglog-hazard for a 1 unit increase in the respective predictor variable. Predictors can be discrete, continuous, and time-varying or time-invariant. For example, the effect of a 1 unit increase in X~1ij~ is to vertically shift the whole baseline cloglog-hazard function by $\beta$~3~ cloglog-hazard units. However, if the predictor interacts linearly with TIME (see X~2ij~ in the example), then the effect of a 1 unit increase in X~2ij~ is to vertically shift the predicted cloglog-hazard in bin 9 by $\beta$~4~ cloglog-hazard units (when TIME-9 = 0), in bin 10 by $\beta$~4~ + $\beta$~5~ cloglog-hazard units (when TIME-9 = 1), and so forth. To interpret the effects of a predictor, its $\beta$ parameter is exponentiated, resulting in a hazard ratio (due to the use of the cloglog link). When using the logit link, exponentiating a $\beta$ parameter results in an odds ratio.

An example (single-level) discrete-time hazard model for individual i in bin t of trial j with a general specification for TIME (separate intercepts for each of six bins, where D1 to D6 are binary indicator variables identifying each bin) and a single predictor (X~1ij~) can be written as follows:

\noindent cloglog[h~ij~(t)] =  [$\beta$~0~D1 + $\beta$~1~D2 + $\beta$~2~D3 + $\beta$~3~D4 + $\beta$~4~D5 + $\beta$~5~D6] + [$\beta$~6~X~1ij~]  \hfill  (7)

@@

To gain a sense of what prior *logit* values would approximate a uniform distribution on the probability scale, @kurzAppliedLongitudinalDataAnalysis2023 simulated a large number of draws from the Uniform(0,1) distribution, converted those draws to the log-odds metric, and fitted a Student's t distribution. Row C in Supplementary Figure 3 shows that using a t-distribution with 7.61 degrees of freedom and a scale parameter of 1.57 as a prior on the logit scale, approximates a uniform distribution on the probability scale. According to @kurzAppliedLongitudinalDataAnalysis2023, such a prior might be a good prior for the intercept(s) in a logit-hazard model, while the N(0,1) prior in row D might be a good prior for the non-intercept parameters in a logit-hazard model, as it gently regularizes p towards .5 (i.e., a zero effect on the logit scale).

@@

## G. Advantages of EHA

### 2025-07-05 manuscript/Suppl_material/supplementary.tex
changes to suppl. material

Studying the effect of stimulus-onset-asynchrony (SOA) on mean RT is still a popular approach to study the time course of cognitive processes (ref). For example, a target stimulus can be presented with a certain SOA in relation to another stimulus (e.g., prime, mask, distractor, cue). However, mean RT conceals the possibe presence of responses triggered by the non-target stimulus (Panis, 2020; Panis \& Schmidt, 2016). For example, in Supplementary Figure 1C a prime is presented before a target with a SOA of -400 ms (upper x-axis labels). To capture responses triggered by the prime (and emitted before target onset) we have to start the timer at trial onset. Also, when RTs are originally recorded relative to target onset, we have to add a constant time to each (here: + 400 ms) in order to include these ``negative'' RTs in the analysis (lower x-axis labels). In general, all RTs must be positive for EHA to work.

Finally, in a bistable perception task (Supplementary Figure 1D), the participant is looking at an ambiguous stimulus (e.g., the duck-rabbit illusion, the Necker cube) for two minutes in each trial, for example, and asked to press a button each time when her/his perception switches from one possibe interpretation to the other possible interpretation. In this task, there are two events (percept A switches to percept B, percept B switches to percept A) that can recur within the same observation period of two minutes, so that the individual transitions back and forth between two states. Note that we do not analyse recurrent events in this tutorial. More information about recurrent events analysis can be found in REF and REF\ldots{}

@@

The shape of a distribution of waiting times can be described in multiple ways (Luce, 1991). After dividing time in discrete, contiguous time bins indexed by t, let RT be a discrete random variable denoting the rank of the time bin in which a particular person's response occurs in a particular experimental condition.
Because waiting times can only increase, discrete-time EHA focuses on the discrete-time hazard function

@@

While psychological RT data is typically measured in small, continuous units (e.g., milliseconds), discrete-time EHA treats the RT data as interval-censored data, because it only uses the information that the response occurred sometime in a particular bin of time (x,y{]}: x \textless{} RT \(\leq\) y. If we want to use the exact event times, then we treat time as a continuous variable, and let RT be a continous random variable denoting a particular person's response time in a particular experimental condition. Continuous-time EHA does not focus on the cumulative distribution function F(t) = P(RT \(\leq\) t) and its derivative, the probability density function f(t) = F(t)', but on the survivor function S(t) = P(RT \(>\) t) and the hazard rate function \(\lambda\)(t) = f(t)/S(t). The hazard rate function gives you the instantaneous \emph{rate} of event occurrence at time point t, given that the event has not occurred yet.

@@

Popular link functions include the logit link and the complementary log-log link, as shown in Supplementary Figure 1.

@@

\caption{The logit and cloglog link functions.}\label{fig:plot-link-functions}
\end{figure}

@@

An example (single-level) discrete-time hazard model with three predictors (TIME, X\textsubscript{1}, X\textsubscript{2}), the cloglog link function, and a second-order polynomial specification for TIME can be written as follows:

\noindent cloglog{[}h(t){]} = ln(-ln{[}1-h(t){]}) = {[}\(\beta\)\textsubscript{0}ONE + \(\beta\)\textsubscript{1}(TIME-9) + \(\beta\)\textsubscript{2}(TIME-9)\(^2\){]} + {[}\(\beta\)\textsubscript{3}X\textsubscript{1} + \(\beta\)\textsubscript{4}X\textsubscript{2} + \(\beta\)\textsubscript{5}X\textsubscript{2}(TIME-9){]} \hfill  (6)

The main predictor variable TIME is the time bin index t that is centered on value 9 in this example. The first set of terms within brackets, the parameters \(\beta\)\textsubscript{0} to \(\beta\)\textsubscript{2} multiplied by their polynomial specifications of (centered) time, represents the shape of the baseline cloglog-hazard function (i.e., when all predictors X\textsubscript{i} take on a value of zero). The second set of terms (the beta parameters \(\beta\)\textsubscript{3} to \(\beta\)\textsubscript{5}) represents the vertical shift in the baseline cloglog-hazard for a 1 unit increase in the respective predictor variable. Predictors can be discrete, continuous, and time-varying or time-invariant. For example, the effect of a 1 unit increase in X\textsubscript{1} is to vertically shift the whole baseline cloglog-hazard function by \(\beta\)\textsubscript{3} cloglog-hazard units. However, if the predictor interacts linearly with TIME (see X\textsubscript{2} in the example), then the effect of a 1 unit increase in X\textsubscript{2} is to vertically shift the predicted cloglog-hazard in bin 9 by \(\beta\)\textsubscript{4} cloglog-hazard units (when TIME-9 = 0), in bin 10 by \(\beta\)\textsubscript{4} + \(\beta\)\textsubscript{5} cloglog-hazard units (when TIME-9 = 1), and so forth. To interpret the effects of a predictor, its \(\beta\) parameter is exponentiated, resulting in a hazard ratio (due to the use of the cloglog link). When using the logit link, exponentiating a \(\beta\) parameter results in an odds ratio.

An example (single-level) discrete-time hazard model with a general specification for TIME (separate intercepts for each of six bins, where D1 to D6 are binary indicator variables identifying each bin) and a single predictor (X\textsubscript{1}) can be written as follows:

\noindent cloglog{[}h(t){]} = {[}\(\beta\)\textsubscript{0}D1 + \(\beta\)\textsubscript{1}D2 + \(\beta\)\textsubscript{2}D3 + \(\beta\)\textsubscript{3}D4 + \(\beta\)\textsubscript{4}D5 + \(\beta\)\textsubscript{5}D6{]} + {[}\(\beta\)\textsubscript{6}X\textsubscript{1}{]} \hfill  (7)

@@

To gain a sense of what prior \emph{logit} values would approximate a uniform distribution on the probability scale, Kurz (2023) simulated a large number of draws from the Uniform(0,1) distribution, converted those draws to the log-odds metric, and fitted a Student's t distribution. Row C in Supplementary Figure 2 shows that using a t-distribution with 7.61 degrees of freedom and a scale parameter of 1.57 as a prior on the logit scale, approximates a uniform distribution on the probability scale. According to Kurz (2023), such a prior might be a good prior for the intercept(s) in a logit-hazard model, while the N(0,1) prior in row D might be a good prior for the non-intercept parameters in a logit-hazard model, as it gently regularizes p towards .5 (i.e., a zero effect on the logit scale).

@@

\subsection{G. Advantages of hazard analysis}\label{g.-advantages-of-hazard-analysis}

@@

>>>>

Studying the effect of stimulus-onset-asynchrony (SOA) on mean RT is still a popular approach to study the time course of cognitive processes. For example, a target stimulus can be presented with a certain SOA in relation to another stimulus (e.g., prime, mask, distractor, cue). However, mean RT conceals the possibe presence of responses triggered by the non-target stimulus (Panis, 2020; Panis \& Schmidt, 2016). For example, in Supplementary Figure 1C a prime is presented before a target with a SOA of -400 ms (upper x-axis labels). To capture responses triggered by the prime (and emitted before target onset) we have to start the timer at trial onset. Also, when RTs are originally recorded relative to target onset, we have to add a constant time to each (here: + 400 ms) in order to include these ``negative'' RTs in the analysis (lower x-axis labels). In general, all RTs must be positive for EHA to work.

Finally, in a bistable perception task (Supplementary Figure 1D), the participant is looking at an ambiguous stimulus (e.g., the duck-rabbit illusion, the Necker cube) for two minutes in each trial, for example, and asked to press a button each time when her/his perception switches from one possibe interpretation to the other possible interpretation. In this task, there are two events (percept A switches to percept B, percept B switches to percept A) that can recur within the same observation period of two minutes, so that the individual transitions back and forth between two states. Note that we do not analyse recurrent events in this tutorial. More information about recurrent events analysis can be found in Stoolmiller and Snyder (2006) and Mills (2011).

@@

The shape of a distribution of waiting times can be described in multiple ways (Luce, 1991). After dividing time in discrete, contiguous time bins indexed by t, let RT be a discrete random variable denoting the rank of the time bin in which a particular person's response occurs in a particular trial.
Because waiting times can only increase, discrete-time EHA focuses on the discrete-time hazard function

@@

While psychological RT data is typically measured in small, continuous units (e.g., milliseconds), discrete-time EHA treats the RT data as interval-censored data, because it only uses the information that the response occurred sometime in a particular bin of time (x,y{]}: x \textless{} RT \(\leq\) y. If we want to use the exact event times, then we treat time as a continuous variable, and let RT be a continous random variable denoting a particular person's response time in a particular experimental condition. Continuous-time EHA does not focus on the cumulative distribution function F(t) = P(RT \(\leq\) t) and its derivative, the probability density function f(t) = F(t)', but on the survivor function S(t) = P(RT \(>\) t) and the hazard rate function \(\lambda\)(t) = f(t)/S(t). The hazard rate function gives you the instantaneous \emph{rate} of event occurrence at time point t, given that the event has not occurred yet. Models for continous-time event data come in three forms: parametric models, Cox regression, and piece-wise exponential models (Singer \& Willett, 2003).

@@

Popular link functions include the logit link and the complementary log-log link, as shown in Supplementary Figure 2.

@@

\caption{The logit and complementary log-log (cloglog) link functions.}\label{fig:plot-link-functions}
\end{figure}

@@

An example (single-level) discrete-time hazard model for individual i in bin t of trial j with three predictors (TIME, X\textsubscript{1}, X\textsubscript{2}), the cloglog link function, and a second-order polynomial specification for TIME can be written as follows:

\noindent cloglog{[}h\textsubscript{ij}(t){]} = ln(-ln{[}1-h\textsubscript{ij}(t){]}) = {[}\(\beta\)\textsubscript{0}ONE + \(\beta\)\textsubscript{1}(TIME-9) + \(\beta\)\textsubscript{2}(TIME-9)\(^2\){]} + {[}\(\beta\)\textsubscript{3}X\textsubscript{1ij} + \(\beta\)\textsubscript{4}X\textsubscript{2ij} + \(\beta\)\textsubscript{5}X\textsubscript{2ij}(TIME-9){]} \hfill  (6)

The main predictor variable TIME is the time bin index t that is centered on value 9 in this example. The first set of terms within brackets, the parameters \(\beta\)\textsubscript{0} to \(\beta\)\textsubscript{2} multiplied by their polynomial specifications of (centered) time, represents the shape of the baseline cloglog-hazard function (i.e., when all predictors X\textsubscript{ij} take on a value of zero). The second set of terms (the beta parameters \(\beta\)\textsubscript{3} to \(\beta\)\textsubscript{5}) represents the vertical shift in the baseline cloglog-hazard for a 1 unit increase in the respective predictor variable. Predictors can be discrete, continuous, and time-varying or time-invariant. For example, the effect of a 1 unit increase in X\textsubscript{1ij} is to vertically shift the whole baseline cloglog-hazard function by \(\beta\)\textsubscript{3} cloglog-hazard units. However, if the predictor interacts linearly with TIME (see X\textsubscript{2ij} in the example), then the effect of a 1 unit increase in X\textsubscript{2ij} is to vertically shift the predicted cloglog-hazard in bin 9 by \(\beta\)\textsubscript{4} cloglog-hazard units (when TIME-9 = 0), in bin 10 by \(\beta\)\textsubscript{4} + \(\beta\)\textsubscript{5} cloglog-hazard units (when TIME-9 = 1), and so forth. To interpret the effects of a predictor, its \(\beta\) parameter is exponentiated, resulting in a hazard ratio (due to the use of the cloglog link). When using the logit link, exponentiating a \(\beta\) parameter results in an odds ratio.

An example (single-level) discrete-time hazard model for individual i in bin t of trial j with a general specification for TIME (separate intercepts for each of six bins, where D1 to D6 are binary indicator variables identifying each bin) and a single predictor (X\textsubscript{1ij}) can be written as follows:

\noindent cloglog{[}h\textsubscript{ij}(t){]} = {[}\(\beta\)\textsubscript{0}D1 + \(\beta\)\textsubscript{1}D2 + \(\beta\)\textsubscript{2}D3 + \(\beta\)\textsubscript{3}D4 + \(\beta\)\textsubscript{4}D5 + \(\beta\)\textsubscript{5}D6{]} + {[}\(\beta\)\textsubscript{6}X\textsubscript{1ij}{]} \hfill  (7)

@@

To gain a sense of what prior \emph{logit} values would approximate a uniform distribution on the probability scale, Kurz (2023) simulated a large number of draws from the Uniform(0,1) distribution, converted those draws to the log-odds metric, and fitted a Student's t distribution. Row C in Supplementary Figure 3 shows that using a t-distribution with 7.61 degrees of freedom and a scale parameter of 1.57 as a prior on the logit scale, approximates a uniform distribution on the probability scale. According to Kurz (2023), such a prior might be a good prior for the intercept(s) in a logit-hazard model, while the N(0,1) prior in row D might be a good prior for the non-intercept parameters in a logit-hazard model, as it gently regularizes p towards .5 (i.e., a zero effect on the logit scale).

@@

\subsection{G. Advantages of EHA}\label{g.-advantages-of-eha}

@@

\bibitem[\citeproctext]{ref-singerAppliedLongitudinalData2003}
Singer, J. D., \& Willett, J. B. (2003). \emph{Applied {Longitudinal Data Analysis}: {Modeling Change} and {Event Occurrence}}. Oxford, New York: Oxford University Press.

\bibitem[\citeproctext]{ref-stoolmillerModelingHeterogeneitySocial2006}
Stoolmiller, M., \& Snyder, J. (2006). Modeling heterogeneity in social interaction processes using multilevel survival analysis. \emph{Psychological Methods}, \emph{11}(2), 164--177. \url{https://doi.org/10.1037/1082-989X.11.2.164}
